### 2021-04-14 paper.Rmd
redo interpolation figure

\begin{figure}
\centering
\includegraphics[width=0.9\textwidth]{figures/notation-2d-space.pdf}
\caption{Still views of a tour showing the space of possible two-dimensional projections as a torus shape in grey, and the trace of two short paths obtained via geodesic interpolation traced in color.}
\label{fig:interpolation-2d}
\end{figure}

@@

This review highlights the history of tour methods, and modern extensions for the visualization of high dimensional numerical data. The rich ecosystem of tours is being actively developed and applied to a broad range of problems including machine learning. When tours are be combined with some interactivity it can assist with analyses like clustering (the spinifex and liminal packages).  Modified displays of projected data can be used to expose local structures (the sage algorithm, slicing and section pursuit). New algorithm data collection inside the tour code is being used to better diagnose optimization procedures for projection pursuit (ferrn).

>>>>

\begin{figure*}[ht]
\centerline{\includegraphics[width=0.2\textwidth]{figures/notation-torus-frames/torus001.png}
\hspace{5mm}
\includegraphics[width=0.2\textwidth]{figures/notation-torus-frames/torus017.png}
\hspace{5mm}
\includegraphics[width=0.2\textwidth]{figures/notation-torus-frames/torus064.png}}
\centerline{
\includegraphics[width=0.2\textwidth]{figures/notation-torus-frames/torus068.png}
\hspace{5mm}
\includegraphics[width=0.2\textwidth]{figures/notation-torus-frames/torus075.png}
\hspace{5mm}
\includegraphics[width=0.2\textwidth]{figures/notation-torus-frames/torus100.png}
}
\caption{Still views of a tour showing the space of possible two-dimensional projections as a torus shape in grey, and the trace of two short paths obtained via geodesic interpolation traced in color.}
\label{fig:interpolation-2d}
\end{figure*}

@@

This review highlights the history of tour methods, and modern extensions for the visualization of high dimensional numerical data. The rich ecosystem of tours is being actively developed and applied to a broad range of problems including machine learning. When tours are be combined with some interactivity it can assist with analyses like clustering (the spinifex and liminal packages).  Modified displays of projected data can be used to expose local structures (the sage algorithm, slicing and section pursuit). New algorithm data collection inside the tour code is being used to better diagnose optimization procedures for projection pursuit [@zhang2021visual].
